Automated Topic Naming

### 2011-08-25 ese/ese.tex

@@

\emph{Internal validity} -- %includes inter-rater reliability and our lack of rival explanation building. 
We improved internal validity by trying to correlate and explain the behaviours observed in the analysis with the historical records of the projects.
We did not attempt to match our results to any particular model.
We assessed inter-rater reliability (IRR) using Cohen's Kappa to measure the level of agreement between the manual 
annotations the first two authors created, under some model of random agreement. Perfect IRR (1.0) indicates 
complete agreement on the appropriate annotation for that topic. We verified IRR using manually annotated PostgreSQL topics, 
and achieved a result of 0.108 (slight agreement), with a correlation coefficient of 0.108. 
Some of the reasons for this are a disagreement over the appropriate classification for documentation topics (should this be considered
usability or portability?), and a disagreement on functionality as a software quality. A short education session on the meaning of a given NFR from 
the ISO standard would reduce this error rate.
In general there is disagreement over what constitutes a non-functional requirement \cite{Glinz_2007}.

>>>>

\subsection{Inter-rater reliability}

Authors Neil and Abram each annotated the PostgreSQL topics in order
to determine inter-rater reliability. While when they read each others
annotations they generally agreed, the inter-rater reliability did not
bear this out.

%>    A_portability   A_functionality     A_reliability A_maintainability
%>      0.153548387      -0.013588517       0.004573794       0.082001031
%>     A_efficiency       A_usability            A_none
%>      0.231496539       0.009287926       0.062133646

% > Spearman says
% >   A_portability   A_functionality     A_reliability A_maintainability
% >      0.253037469      -0.014415214       0.004579664       0.082215613
% >     A_efficiency       A_usability            A_none
% >      0.258037216       0.014436230       0.080667468

\begin{table}
\centering
\begin{tabular}{l|c|c}
\hline
            & Cohen's Kappa & Spearman Correlation \\ \hline
Portability & 0.154 & 0.253  \\
Functionality & -0.014 & -0.014 \\
Reliability & 0.005 & 0.005 \\
Maintainability & 0.082 & 0.082 \\
Efficiency & 0.231 & 0.258 \\
Usability & 0.009 & 0.014 \\
None &      0.062 & 0.081 \\ \hline 
Everything & 0.107 & 0.108 \\ \hline
\end{tabular}
\caption{Inter-rater Reliability on PostgreSQL}
\label{tab:interr}
\end{table}

Table \ref{tab:iterr} describes the Cohen Kappa and the Spearman
correlation of our per topic annotations for each tag. We had to
evaluate inter-rater reliability this way because 1 topic could be
tagged with more than 1 annotation.

We feel these results are poor. The aggregate view of with a Kappa of
$0.1$ indicates there is some agreement but not a lot. We found that
there was a lot of agreement in terms of lack of a tag, but often more
disagreement when a tag should be applied.

After some discussion we concluded that usability was a source of
disagreement. Do user manuals improve usability? Is a command-line
option a usability issue? These kinds of questions illustrate some of
the agreement, disagreement and ambiguity about these labels. Further
more, both annotators found that the annotation was time-consuming and
difficult.

% I think this is largely due to lack of training. So I will write it up as such - as an interesting point to say that agreeing on the meaning of "software quality" is difficult, etc. Ideally we would now do a sample training session where we go over say one period and determine the appropriate annotations, then recalculate Kappa to see what changes.

% The other tack is to ignore the IRR data completely as we did in the workshop. But I don't think it hurts our results that much ¦ just confirms the difficulty of annotation.

% Neil

@@

\emph{Internal validity} -- %includes inter-rater reliability and our lack of rival explanation building. 
We improved internal validity by trying to correlate and explain the behaviours observed in the analysis with the historical records of the projects.
We did not attempt to match our results to any particular model.
We assessed inter-rater reliability (IRR) using Cohen's Kappa to measure the level of agreement between the manual 
annotations the first two authors created, under some model of random agreement. Perfect IRR (1.0) indicates 
complete agreement on the appropriate annotation for that topic. We verified IRR using manually annotated PostgreSQL topics, 
and achieved a result of 0.108 (slight agreement), with a correlation coefficient of 0.108.

Some of the reasons for this are a disagreement over the appropriate classification for documentation topics (should this be considered
usability or portability?), and a disagreement on functionality as a software quality. A short education session on the meaning of a given NFR from 
the ISO standard would reduce this error rate.
In general there is disagreement over what constitutes a non-functional requirement \cite{Glinz_2007}.
